### 2018-07-25 doc/plos/text/manuscript.tex
add RelMAE, reword MASE

In a given location over a given period of time, we assess the standalone
accuracy of a nowcast by two measures: mean absolute error (MAE) root mean
squared error (RMSE). With ground truth vector $\vec{x}$, nowcast vector
$\vec{y}$, and elements indexed by week $w$ of $n$, these measures are defined
as:

@@

Although the units of ground truth (i.e. wILI) are the same in all locations,
the normal range of wILI varies between locations. To facilitate comparison
between locations, we also report mean absolute scaled error (MASE)
\cite{hyndman2006another}. MASE is the MAE of a given nowcast normalized by the
MAE of a one-step naive nowcast computed in-sample in the same location.

Because wILI is subject to revision over multiple months, a real-time naive
nowcast would be defined as \textit{preliminary} wILI on the preceding week.
However, preliminary versions of wILI are not generally known today (except for
within a narrow set of locations and seasons). As a result, we introduce the
``Naive Oracle'' nowcaster. This assumes (incorrectly) that the final version
of wILI is known with no delay and defines the naive nowcast as \textit{final}
wILI on the preceding week. Since this information is not available at runtime,
the Naive Oracle is unfairly advantaged. As such, MASE is reasonably subject to
being greater than one, indicating that the nowcast under consideration
performed \textit{worse} than the ``naive'' nowcast. This should be
unsurprising, if not expected, given that the Naive Oracle incorporates
information which is not available at runtime. In any case, MASE is a useful
measure for comparing the performance of a given nowcast across different
locations.

Given the above discussion of the Naive Oracle, we define the naive nowcast for
any given location on any given week as the final value of ground truth in the
same location one week earlier. Using the same notation as above, and
considering the $m$ weeks for which ground truth is available on the prior
week, MASE is defined as:

\begin{align*}
  \text{MASE} &= \text{MAE} \left( \frac{1}{m} \sum_{w=1}^m{\left|x_w - x_{w - 1}\right|} \right) ^ {-1}
\end{align*}

@@

>>>>

In a given location over a given period of time, we assess the absolute
(scale-dependent) error of a nowcast by two measures: mean absolute error (MAE)
and root mean squared error (RMSE). With ground truth vector $\vec{x}$, nowcast
vector $\vec{y}$, and elements indexed by week $w$ of $n$, these measures are
defined as:

@@

Although the units of ground truth (i.e. wILI) are the same in all locations,
the normal range of wILI varies between locations. To facilitate aggregation
and comparison among locations, we report several relative (scale-independent)
error measures with respect to various baselines. Each of these is computed by
normalizing nowcast error by the same type of error measured on the output of a
baseline model. Here we define two such baseline models: ``naive'' and
``simple''.

Because wILI is subject to revision over multiple months, a real-time naive
nowcast would be defined as \textit{preliminary} wILI on the preceding week.
However, preliminary versions of wILI are not generally known today (except for
within a narrow set of locations and seasons). As a result, we introduce a
``naive oracle'' nowcaster. This assumes (incorrectly) that the final version
of wILI is known with no delay and defines the naive nowcast as \textit{final}
wILI on the preceding week. Since this information is not available at runtime,
the naive baseline is unfairly advantaged.

The ``simple'' baseline is defined as the median of all sensor readings for a
given location, ignoring sensor readings elsewhere. This is in effect a wisdom
of the crowd nowcast that doesn't incorporate information from outside
locations.

We report MAE of nowcasts relative to MAE of each baseline (RelMAE TODO(cite)).
In doing so with the ``naive'' baseline, this is a special case of RelMAE known
as mean absolute scaled error (MASE) \cite{hyndman2006another}. MASE is defined
in the context of time-series forecasting in general as the MAE of a given forecast
normalized by the MAE of an in-sample, one-step naive forecast.

Using the same notation as above, assuming $\tilde{z}_w$ represents the median
sensor reading for the current location on week $w$, and considering the $m$
weeks for which ground truth is available on the prior week, these measures are
defined as:

\begin{align*}
  \text{RelMAE} &= \text{MAE} \left( \frac{1}{n} \sum_{w=1}^n{\left|x_w - \tilde{z}_w\right|} \right) ^ {-1} \\
  \text{MASE} &= \text{MAE} \left( \frac{1}{m} \sum_{w=1}^m{\left|x_w - x_{w - 1}\right|} \right) ^ {-1}
\end{align*}

@@

MASE is reasonably subject to being greater than one, indicating that the
nowcast under consideration performed \textit{worse} than the ``naive''
nowcast. This should be unsurprising, if not expected, given that the naive
oracle incorporates information which is not available at runtime.
